Linearizability Proofs Based On Forward Simulations

### 2017-01-20 draftCAV/stack.tex
started stacks

We consider a set of actions $Com(pop)=\set{com(pop,d,k):d\in\<Vals>, k\in\<Ops>}$, called \emph{commit points}, representing actions of a pop operation where its return value is determined. Usually, a stack implementation stores the pushed values into a data structure, e.g., a singly-linked list, and a pop operation contains an action (typically, a compare-and-swap) that removes an element from this data structure (or sets a flag associated to this element to a ``deleted'' state). Such an action represents a commit point since the pop operation will return the value stored in this element.

>>>>

\begin{wrapfigure}{l}{6.1cm}
\vspace{-14mm}
\begin{lstlisting}
struct Node{
  int data;
  int ts;
  Node* next;
  boolean taken;
};
Node* pools[maxThreads];
int TS = 0;

void push(int x) {
  Node* n = new Node(x,MAX_INT,
                        null,false);
  n->next = pools[myTID];
  pools[myTID] = n;
  int i = TS++;
  n->ts = i;
}
int pop() {
  boolean success = false;
  int maxTS = -1;
  Node* youngest = null;
  while ( !success ) {
    maxTS = -1; youngest = null;
    for(int i = 0; i < maxThreads; i++){
      Node* n = pools[i];
      while (n->taken && n->next != null)
        n = n->next;
      if(maxTS < n->ts) {
        maxTS = n->ts; youngest = n;
      }
    }
    success=CAS(youngest->taken,false,true);
  }
  return youngest;
}
\end{lstlisting}
\vspace{-6mm}
\caption{Time-Stamped Stack. We assume that every statement is atomic.}
\label{fig:HerlihyWing}
\vspace{-1mm}
\end{wrapfigure}
We consider a set of actions $Com(pop)=\set{com(pop,d,k):d\in\<Vals>, k\in\<Ops>}$, called \emph{commit points}, representing actions of a pop operation where its return value is determined. Usually, a stack implementation stores the pushed values into a data structure, e.g., a singly-linked list, and a pop operation contains an action (typically, a compare-and-swap) that removes an element from this data structure (or sets a flag associated to this element to a ``deleted'' state). Such an action represents a commit point since the pop operation will return the value stored in this element.

// Initially each pool[i] points to a 
// sentinel dummy node with ts = -1, 
// next = null, taken=false
